---
title: "2022 DHS Data Extraction"
author: "Anita Makori"
date: "2023-01-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prep
```{r}
require(pacman)
p_load(docxtractr)
p_load(dplyr)
p_load(tidyverse)
p_load(ggiraph)

# import all the tables
dhs2022report <- read_docx("2022KDHSKIR_KNBS.docx") 

# number of tables in the report
docx_tbl_count(dhs2022report)
tbls <- docx_extract_all_tbls(dhs2022report, trim = T, guess_header = T)
```

## 3.13	Child Nutritional Status

### Table 14: Nutritional status of children
```{r}
## by age 
nut_age_hfa <- tbls[[52]]%>%
  slice(6:11,13,14) %>%
  dplyr::select(V1:V5)%>%
  dplyr::rename(Age = V1, perc_below3sd = V2, perc_below2sd = V3, zscore= V4, no = V5)%>%
  dplyr::mutate(indicator = "HFA")

nut_age_wfh <- tbls[[52]]%>%
  slice(6:11,13,14) %>%
  dplyr::select(V1,V6,V7,V9,V10)%>%
  dplyr::rename(Age = V1, perc_below3sd = V6, perc_below2sd = V7, zscore= V9, no = V10)%>%
  dplyr::mutate(indicator = "WFH")

nut_age_wfa <- tbls[[52]]%>%
  slice(6:11,13,14) %>%
  dplyr::select(V1,V11:V14)%>%
  dplyr::rename(Age = V1, perc_below3sd = V11, perc_below2sd = V12, zscore= V13, no = V14)%>%
  dplyr::mutate(indicator = "WFA")

nut_age <- dplyr::bind_rows(nut_age_hfa, nut_age_wfh, nut_age_wfa)
write_csv(nut_age, "table14_nutr_status_by_age.csv")

## by sex
nut_sex_hfa <- tbls[[52]]%>%
  slice(17:18) %>%
  dplyr::select(V1:V5)%>%
  dplyr::rename(Sex = V1, perc_below3sd = V2, perc_below2sd = V3, zscore= V4, no = V5)%>%
  dplyr::mutate(indicator = "HFA")

nut_sex_wfh <- tbls[[52]]%>%
  slice(17:18) %>%
  dplyr::select(V1,V6,V7,V9,V10)%>%
  dplyr::rename(Sex = V1, perc_below3sd = V6, perc_below2sd = V7, zscore= V9, no = V10)%>%
  dplyr::mutate(indicator = "WFH")

nut_sex_wfa <- tbls[[52]]%>%
  slice(17:18) %>%
  dplyr::select(V1,V11:V14)%>%
  dplyr::rename(Sex = V1, perc_below3sd = V11, perc_below2sd = V12, zscore= V13, no = V14)%>%
  dplyr::mutate(indicator = "WFA")

nut_sex <- dplyr::bind_rows(nut_sex_hfa, nut_sex_wfh, nut_sex_wfa)
write_csv(nut_sex, "table14_nutr_status_by_sex.csv")

## by residence
nut_res_hfa <- tbls[[52]]%>%
  slice(26:27) %>%
  dplyr::select(V1:V5)%>%
  dplyr::rename(Residence = V1, perc_below3sd = V2, perc_below2sd = V3, zscore= V4, no = V5)%>%
  dplyr::mutate(indicator = "HFA")

nut_res_wfh <- tbls[[52]]%>%
  slice(26:27) %>%
  dplyr::select(V1,V6,V7,V9,V10)%>%
  dplyr::rename(Residence = V1, perc_below3sd = V6, perc_below2sd = V7, zscore= V9, no = V10)%>%
  dplyr::mutate(indicator = "WFH")

nut_res_wfa <- tbls[[52]]%>%
  slice(26:27) %>%
  dplyr::select(V1,V11:V14)%>%
  dplyr::rename(Residence = V1, perc_below3sd = V11, perc_below2sd = V12, zscore= V13, no = V14)%>%
  dplyr::mutate(indicator = "WFA")

nut_res <- dplyr::bind_rows(nut_res_hfa, nut_res_wfh, nut_res_wfa)
write_csv(nut_res, "table14_nutr_status_by_residence.csv")

## by mot edu
nut_motedu_hfa <- tbls[[52]]%>%
  slice(30:33) %>%
  dplyr::select(V1:V5)%>%
  dplyr::rename(`Mother's education` = V1, perc_below3sd = V2, perc_below2sd = V3, zscore= V4, no = V5)%>%
  dplyr::mutate(indicator = "HFA")

nut_motedu_wfh <- tbls[[52]]%>%
  slice(30:33) %>%
  dplyr::select(V1,V6,V7,V9,V10)%>%
  dplyr::rename(`Mother's education` = V1, perc_below3sd = V6, perc_below2sd = V7, zscore= V9, no = V10)%>%
  dplyr::mutate(indicator = "WFH")

nut_motedu_wfa <- tbls[[52]]%>%
  slice(30:33) %>%
  dplyr::select(V1,V11:V14)%>%
  dplyr::rename(`Mother's education` = V1, perc_below3sd = V11, perc_below2sd = V12, zscore= V13, no = V14)%>%
  dplyr::mutate(indicator = "WFA")

nut_motedu <- dplyr::bind_rows(nut_motedu_hfa, nut_motedu_wfh, nut_motedu_wfa)
write_csv(nut_motedu, "table14_nutr_status_by_mother_edu.csv")

## by wealth
nut_wealth_hfa <- tbls[[52]]%>%
  slice(36:40) %>%
  dplyr::select(V1:V5)%>%
  dplyr::rename(`Wealth quintile` = V1, perc_below3sd = V2, perc_below2sd = V3, zscore= V4, no = V5)%>%
  dplyr::mutate(indicator = "HFA")

nut_wealth_wfh <- tbls[[52]]%>%
  slice(36:40) %>%
  dplyr::select(V1,V6,V7,V9,V10)%>%
  dplyr::rename(`Wealth quintile` = V1, perc_below3sd = V6, perc_below2sd = V7, zscore= V9, no = V10)%>%
  dplyr::mutate(indicator = "WFH")

nut_wealth_wfa <- tbls[[52]]%>%
  slice(36:40) %>%
  dplyr::select(V1,V11:V14)%>%
  dplyr::rename(`Wealth quintile` = V1, perc_below3sd = V11, perc_below2sd = V12, zscore= V13, no = V14)%>%
  dplyr::mutate(indicator = "WFA")

nut_wealth <- dplyr::bind_rows(nut_wealth_hfa, nut_wealth_wfh, nut_wealth_wfa)
write_csv(nut_wealth, "table14_nutr_status_by_wealth.csv")
```

### Table 14C: Nutritional status of children by county
```{r}
nutc_hfa <- tbls[[53]]%>%
  slice(5:51) %>%
  dplyr::select(V1:V5)%>%
  dplyr::rename(`County` = V1, perc_below3sd = V2, perc_below2sd = V3, zscore= V4, no = V5)%>%
  dplyr::mutate(indicator = "HFA")

nutc_wfh <- tbls[[53]]%>%
  slice(5:51) %>%
  dplyr::select(V1,V6,V7,V9,V10)%>%
  dplyr::rename(`County` = V1, perc_below3sd = V6, perc_below2sd = V7, zscore= V9, no = V10)%>%
  dplyr::mutate(indicator = "WFH")

nutc_wfa <- tbls[[53]]%>%
  slice(5:51) %>%
  dplyr::select(V1,V11:V14)%>%
  dplyr::rename(`County` = V1, perc_below3sd = V11, perc_below2sd = V12, zscore= V13, no = V14)%>%
  dplyr::mutate(indicator = "WFA")

nutc <- dplyr::bind_rows(nutc_hfa, nutc_wfh, nutc_wfa)
write_csv(nutc, "table14C_nutr_status_by_county.csv")
```

## 3.14	Infant and Young Child Feeding

### Table 15: Infant and young child feeding (IYCF) indicators
```{r}
iycf <- tbls[[59]]
```

## 3.16: Malaria

### Table 18: Household possession of insecticide-treated nets
```{r}
itn_res <- tbls[[67]]%>%
  slice(5,6)%>%
  dplyr::rename(Residence = V1, perc_atleast_1itn = V2, avrg_itn_hh = V3, no_hhs= V4, perc_atleast_1itn_2pple= V5, no_hhs_1person_overnight=V6)

write_csv(itn_res, "table18_ITN_by_residence.csv")

itn_endem <- tbls[[67]]%>%
  slice(9:13)%>%
  dplyr::rename(`Endemicity zone` = V1, perc_atleast_1itn = V2, avrg_itn_hh = V3, no_hhs= V4, perc_atleast_1itn_2pple= V5, no_hhs_1person_overnight=V6)

write_csv(itn_endem, "table18_ITN_by_endemicity_zone.csv")

itn_wealth <- tbls[[67]]%>%
  slice(16:20)%>%
  dplyr::rename(`Wealth quintile` = V1, perc_atleast_1itn = V2, avrg_itn_hh = V3, no_hhs= V4, perc_atleast_1itn_2pple= V5, no_hhs_1person_overnight=V6)

write_csv(itn_wealth, "table18_ITN_by_wealth_quintile.csv")
```

### Table 18C: Household possession of insecticide-treated nets by county
```{r}
itnc <- tbls[[68]]%>%
  slice(4:50)%>%
  dplyr::rename(County = V1, perc_atleast_1itn = V2, avrg_itn_hh = V3, no_hhs= V4, perc_atleast_1itn_2pple= V5, no_hhs_1person_overnight=V6)

write_csv(itnc, "table18C_ITN_by_county.csv")
```



### Table 2C: Background xtics by county

```{r}
### women
women_background_xtics_county <- tbls[[6]]%>%
  slice(5:51)%>%
  select(V1:V4)%>%
  dplyr::rename(County = V1, weighted_perc = V2, weighted_no = V3, unweighted_no = V4)%>%
  mutate(County=recode(County,"Tharaka-Nithi"="Tharaka Nithi", "Elgeyo/Marakwet"="Elgeyo Marakwet","Murang’a"="Muranga",
                       "Nairobi City"="Nairobi","Taita/Taveta"="Taita Taveta"))

write_csv(women_background_xtics_county, "table2C_women_backgroundxtics_by_county.csv")

### men
men_background_xtics_county <- tbls[[6]]%>%
  slice(5:51)%>%
  select(V1,V5:V7)%>%
  dplyr::rename(County = V1, weighted_perc = V5, weighted_no = V6, unweighted_no = V7)%>%
  mutate(County=recode(County,"Tharaka-Nithi"="Tharaka Nithi", "Elgeyo/Marakwet"="Elgeyo Marakwet","Murang’a"="Muranga",
                       "Nairobi City"="Nairobi","Taita/Taveta"="Taita Taveta"))

write_csv(men_background_xtics_county, "table2C_men_backgroundxtics_by_county.csv")
```

### Table 10: Maternal care indicators by background xtics

```{r}
### Mother's age at birth
matcare_motage_1birth <- tbls[[33]]%>%
  slice(7:9)%>%
  select(V1:V5,V7,V8,V10)%>%
  dplyr::rename(`Mother's age at birth`=V1, `ANC from skilled provider`=V2, `At least 4 ANC visits`=V3, `Took iron supplements`=V4, `Protected against neonatal tetanus`=V5, `Delivered by skilled provider` =V7, `Delivered in health facility`=V8, `PNC 2 days after birth`=V10)%>%
  pivot_longer(cols = c(`ANC from skilled provider`:`PNC 2 days after birth`), names_to = "category", values_to = "proportion")

write_csv(matcare_motage_1birth, "table10_maternalcare_by_motherage_atbirth.csv")

### Residence
matcare_residence <- tbls[[33]]%>%
  slice(12:13)%>%
  select(V1:V5,V7,V8,V10)%>%
  dplyr::rename(Residence=V1, `ANC from skilled provider`=V2, `At least 4 ANC visits`=V3, `Took iron supplements`=V4, `Protected against neonatal tetanus`=V5, `Delivered by skilled provider` =V7, `Delivered in health facility`=V8, `PNC 2 days after birth`=V10)%>%
  pivot_longer(cols = c(`ANC from skilled provider`:`PNC 2 days after birth`), names_to = "category", values_to = "proportion")

write_csv(matcare_residence, "table10_maternalcare_by_residence.csv")

### Mother's education
matcare_motedu <- tbls[[33]]%>%
  slice(16:19)%>%
  select(V1:V5,V7,V8,V10)%>%
  dplyr::rename(`Mother's education`=V1, `ANC from skilled provider`=V2, `At least 4 ANC visits`=V3, `Took iron supplements`=V4, `Protected against neonatal tetanus`=V5, `Delivered by skilled provider` =V7, `Delivered in health facility`=V8, `PNC 2 days after birth`=V10)%>%
  pivot_longer(cols = c(`ANC from skilled provider`:`PNC 2 days after birth`), names_to = "category", values_to = "proportion")

write_csv(matcare_motedu, "table10_maternalcare_by_education.csv")

### Wealth
matcare_wealth <- tbls[[33]]%>%
  slice(22:26)%>%
  select(V1:V5,V7,V8,V10)%>%
  dplyr::rename(`Wealth quintile`=V1, `ANC from skilled provider`=V2, `At least 4 ANC visits`=V3, `Took iron supplements`=V4, `Protected against neonatal tetanus`=V5, `Delivered by skilled provider` =V7, `Delivered in health facility`=V8, `PNC 2 days after birth`=V10)%>%
  pivot_longer(cols = c(`ANC from skilled provider`:`PNC 2 days after birth`), names_to = "category", values_to = "proportion")

write_csv(matcare_wealth, "table10_maternalcare_by_wealth.csv")
```

### Table 12: Treatment for ARI symptoms, fever, & diarrhea

```{r}
### Age
treatment_age_ARI <- tbls[[45]]%>%
  slice(6:11)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(Age=V1, sought_treatment=V2)%>%
  mutate(condition="ARI")
treatment_age_fever <- tbls[[45]]%>%
  slice(6:11)%>%
  dplyr::select(V1,V4)%>%
  dplyr::rename(Age=V1, sought_treatment=V4)%>%
  mutate(condition="Fever")
treatment_age_diarrhea <- tbls[[45]]%>%
  slice(6:11)%>%
  dplyr::select(V1,V6)%>%
  dplyr::rename(Age=V1, sought_treatment=V6)%>%
  mutate(condition="Diarrhea")
treatment_age <- rbind(treatment_age_ARI, treatment_age_fever, treatment_age_diarrhea)%>%
  mutate(sought_treatment=gsub("[()]", "", sought_treatment))

write_csv(treatment_age, "table12_childtreatment_by_age.csv")
  
### Sex
treatment_sex_ARI <- tbls[[45]]%>%
  slice(14:15)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(Sex=V1, sought_treatment=V2)%>%
  mutate(condition="ARI")
treatment_sex_fever <- tbls[[45]]%>%
  slice(14:15)%>%
  dplyr::select(V1,V4)%>%
  dplyr::rename(Sex=V1, sought_treatment=V4)%>%
  mutate(condition="Fever")
treatment_sex_diarrhea <- tbls[[45]]%>%
  slice(14:15)%>%
  dplyr::select(V1,V6)%>%
  dplyr::rename(Sex=V1, sought_treatment=V6)%>%
  mutate(condition="Diarrhea")
treatment_sex <- rbind(treatment_sex_ARI, treatment_sex_fever, treatment_sex_diarrhea)%>%
  mutate(sought_treatment=gsub("[()]", "", sought_treatment))

write_csv(treatment_sex, "table12_childtreatment_by_sex.csv")

### Residence
treatment_residence_ARI <- tbls[[45]]%>%
  slice(18:19)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(Residence=V1, sought_treatment=V2)%>%
  mutate(condition="ARI")
treatment_residence_fever <- tbls[[45]]%>%
  slice(18:19)%>%
  dplyr::select(V1,V4)%>%
  dplyr::rename(Residence=V1, sought_treatment=V4)%>%
  mutate(condition="Fever")
treatment_residence_diarrhea <- tbls[[45]]%>%
  slice(18:19)%>%
  dplyr::select(V1,V6)%>%
  dplyr::rename(Residence=V1, sought_treatment=V6)%>%
  mutate(condition="Diarrhea")
treatment_residence <- rbind(treatment_residence_ARI, treatment_residence_fever, treatment_residence_diarrhea)%>%
  mutate(sought_treatment=gsub("[()]", "", sought_treatment))

write_csv(treatment_residence, "table12_childtreatment_by_residence.csv")

### Mother's education
treatment_motedu_ARI <- tbls[[45]]%>%
  slice(22:25)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(`Mother's education`=V1, sought_treatment=V2)%>%
  mutate(condition="ARI")
treatment_motedu_fever <- tbls[[45]]%>%
  slice(22:25)%>%
  dplyr::select(V1,V4)%>%
  dplyr::rename(`Mother's education`=V1, sought_treatment=V4)%>%
  mutate(condition="Fever")
treatment_motedu_diarrhea <- tbls[[45]]%>%
  slice(22:25)%>%
  dplyr::select(V1,V6)%>%
  dplyr::rename(`Mother's education`=V1, sought_treatment=V6)%>%
  mutate(condition="Diarrhea")
treatment_motedu <- rbind(treatment_motedu_ARI, treatment_motedu_fever, treatment_motedu_diarrhea)%>%
  mutate(sought_treatment=gsub("[()]", "", sought_treatment))

write_csv(treatment_motedu, "table12_childtreatment_by_mothereducation.csv")

### Wealth
treatment_wealth_ARI <- tbls[[45]]%>%
  slice(28:32)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(`Wealth quintile`=V1, sought_treatment=V2)%>%
  mutate(condition="ARI")
treatment_wealth_fever <- tbls[[45]]%>%
  slice(28:32)%>%
  dplyr::select(V1,V4)%>%
  dplyr::rename(`Wealth quintile`=V1, sought_treatment=V4)%>%
  mutate(condition="Fever")
treatment_wealth_diarrhea <- tbls[[45]]%>%
  slice(28:32)%>%
  dplyr::select(V1,V6)%>%
  dplyr::rename(`Wealth quintile`=V1, sought_treatment=V6)%>%
  mutate(condition="Diarrhea")
treatment_wealth <- rbind(treatment_wealth_ARI, treatment_wealth_fever, treatment_wealth_diarrhea)%>%
  mutate(sought_treatment=gsub("[()]", "", sought_treatment))

write_csv(treatment_wealth, "table12_childtreatment_by_wealth.csv")
```

### Table 12C: Treatment for ARI symptoms, fever, & diarrhea by county

```{r}
treatment_county_ARI <- tbls[[46]]%>%
  slice(5:51)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(County=V1, sought_treatment=V2)%>%
  mutate(condition="ARI")
treatment_county_fever <- tbls[[46]]%>%
  slice(5:51)%>%
  dplyr::select(V1,V4)%>%
  dplyr::rename(County=V1, sought_treatment=V4)%>%
  mutate(condition="Fever")
treatment_county_diarrhea <- tbls[[46]]%>%
  slice(5:51)%>%
  dplyr::select(V1,V6)%>%
  dplyr::rename(County=V1, sought_treatment=V6)%>%
  mutate(condition="Diarrhea")
treatment_county <- rbind(treatment_county_ARI, treatment_county_fever, treatment_county_diarrhea)%>%
  mutate(sought_treatment=gsub("[()]", "", sought_treatment))%>%
  mutate(sought_treatment=ifelse(sought_treatment%in%"*",NA,sought_treatment))

readr::write_csv(treatment_county, "table12C_childtreatment_by_county.csv")
  
```

### Table 13: Early Childhood Development 2030

### Proportion of children aged 24-59 months who are developmentally on track in health, learning, & psychosocial wellbeing.

```{r}
ecd_age <- tbls[[48]]%>%
  slice(5:7)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(Age=V1, proportion=V2)

readr::write_csv(ecd_age, "table13_ECD_by_age.csv")

ecd_sex <- tbls[[48]]%>%
  slice(10:11)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(Sex=V1, proportion=V2)

readr::write_csv(ecd_sex, "table13_ECD_by_sex.csv")

ecd_residence <- tbls[[48]]%>%
  slice(14:15)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(Residence=V1, proportion=V2)

readr::write_csv(ecd_residence, "table13_ECD_by_residence.csv")

ecd_edu_attendance <- tbls[[48]]%>%
  slice(18:20)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(`Early childhood education attendance`=V1, proportion=V2)

readr::write_csv(ecd_edu_attendance, "table13_ECD_by_early_education_attendance.csv")

ecd_mot_edu <- tbls[[48]]%>%
  slice(23:26)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(`Mother's education`=V1, proportion=V2)

readr::write_csv(ecd_mot_edu, "table13_ECD_by_mother_education.csv")

ecd_wealth <- tbls[[48]]%>%
  slice(29:33)%>%
  dplyr::select(V1,V2)%>%
  dplyr::rename(`Wealth quintile`=V1, proportion=V2)

readr::write_csv(ecd_wealth, "table13_ECD_by_wealth.csv")
  
```

### Table 17: Five-year early childhood mortality rates according to background characteristics	

```{r}
child_mortality_sex <- tbls[[63]]%>%
  slice(5:6)%>%
  dplyr::rename(Sex=V1, `Neonatal Mortality`=V2, `Postneonatal mortality`=V3, `Infant mortality`=V4, `Child mortality`=V5, `Under 5 mortality`=V6 )%>%
  pivot_longer(cols = c(`Neonatal Mortality`:`Under 5 mortality`), names_to = "Measure", values_to = "Value")

readr::write_csv(child_mortality_sex, "table17_child_mortality_by_sex.csv")

child_mortality_residence <- tbls[[63]]%>%
  slice(5:6)%>%
  dplyr::rename(Residence=V1, `Neonatal Mortality`=V2, `Postneonatal mortality`=V3, `Infant mortality`=V4, `Child mortality`=V5, `Under 5 mortality`=V6 )%>%
  pivot_longer(cols = c(`Neonatal Mortality`:`Under 5 mortality`), names_to = "Measure", values_to = "Value")

readr::write_csv(child_mortality_residence, "table17_child_mortality_by_residence.csv")
```

### Table 19: Use of insecticide-treated nets by children and pregnant women	

```{r}
itn_usage_res_children <- tbls[[69]]%>%
  slice(6:7)%>%
  dplyr::select(V1,V2,V4)%>%
  dplyr::rename(Residence=V1, `All households`=V2, `Households with 1+ ITN`=V4)%>%
  pivot_longer(cols=c(`All households`, `Households with 1+ ITN`), names_to="Category", values_to="Proportion")%>%
  mutate(Participants="Children")
itn_usage_res_mothers <- tbls[[69]]%>%
  slice(6:7)%>%
  dplyr::select(V1,V6,V8)%>%
  dplyr::rename(Residence=V1, `All households`=V6, `Households with 1+ ITN`=V8)%>%
  pivot_longer(cols=c(`All households`, `Households with 1+ ITN`), names_to="Category", values_to="Proportion")%>%
  mutate(Participants="Mothers")
itn_usage_res <- rbind(itn_usage_res_children, itn_usage_res_mothers)
readr::write_csv(itn_usage_res, "table19_ITN_usage_children_mothers_by_residence.csv")

itn_usage_endem_children <- tbls[[69]]%>%
  slice(10:14)%>%
  dplyr::select(V1,V2,V4)%>%
  dplyr::rename(`Endemicity zone`=V1, `All households`=V2, `Households with 1+ ITN`=V4)%>%
  pivot_longer(cols=c(`All households`, `Households with 1+ ITN`), names_to="Category", values_to="Proportion")%>%
  mutate(Participants="Children")
itn_usage_endem_mothers <- tbls[[69]]%>%
  slice(10:14)%>%
  dplyr::select(V1,V6,V8)%>%
  dplyr::rename(`Endemicity zone`=V1, `All households`=V6, `Households with 1+ ITN`=V8)%>%
  pivot_longer(cols=c(`All households`, `Households with 1+ ITN`), names_to="Category", values_to="Proportion")%>%
  mutate(Participants="Mothers")
itn_usage_endem <- rbind(itn_usage_endem_children, itn_usage_endem_mothers)
readr::write_csv(itn_usage_endem, "table19_ITN_usage_children_mothers_by_endemicity_zone.csv")  

itn_usage_wealth_children <- tbls[[69]]%>%
  slice(17:21)%>%
  dplyr::select(V1,V2,V4)%>%
  dplyr::rename(`Wealth quintile`=V1, `All households`=V2, `Households with 1+ ITN`=V4)%>%
  pivot_longer(cols=c(`All households`, `Households with 1+ ITN`), names_to="Category", values_to="Proportion")%>%
  mutate(Participants="Children")
itn_usage_wealth_mothers <- tbls[[69]]%>%
  slice(17:21)%>%
  dplyr::select(V1,V6,V8)%>%
  dplyr::rename(`Wealth quintile`=V1, `All households`=V6, `Households with 1+ ITN`=V8)%>%
  pivot_longer(cols=c(`All households`, `Households with 1+ ITN`), names_to="Category", values_to="Proportion")%>%
  mutate(Participants="Mothers")
itn_usage_wealth <- rbind(itn_usage_wealth_children, itn_usage_wealth_mothers)
readr::write_csv(itn_usage_wealth, "table19_ITN_usage_children_mothers_by_wealth.csv") 
```

### Table 19C:	Use of insecticide-treated nets by children and pregnant women by county	
```{r}
itn_usage_county_children <- tbls[[70]]%>%
  slice(5:51)%>%
  dplyr::select(V1,V2,V4)%>%
  dplyr::rename(County=V1, `All households`=V2, `Households with 1+ ITN`=V4)%>%
  pivot_longer(cols=c(`All households`, `Households with 1+ ITN`), names_to="Category", values_to="Proportion")%>%
  mutate(Participants="Children")
itn_usage_county_mothers <- tbls[[70]]%>%
  slice(5:51)%>%
  dplyr::select(V1,V6,V8)%>%
  dplyr::rename(County=V1, `All households`=V6, `Households with 1+ ITN`=V8)%>%
  pivot_longer(cols=c(`All households`, `Households with 1+ ITN`), names_to="Category", values_to="Proportion")%>%
  mutate(Participants="Mothers")
itn_usage_county <- rbind(itn_usage_county_children, itn_usage_county_mothers)%>%
  mutate(County=recode(County,"Tharaka-Nithi"="Tharaka Nithi", "Elgeyo/Marakwet"="Elgeyo Marakwet","Murang’a"="Muranga",
                       "Nairobi City"="Nairobi","Taita/Taveta"="Taita Taveta"))%>%
  mutate(Proportion=gsub("[()]", "", Proportion))%>%
  mutate(Proportion=ifelse(Proportion%in%"*",NA,Proportion))
  
readr::write_csv(itn_usage_county, "table19C_ITN_usage_children_mothers_by_county.csv")
```

### Table 20: Use of intermittent preventive treatment (IPTp) by women during pregnancy	

```{r}
IPTp_res <- tbls[[72]]%>%
  slice(6:7)%>%
  dplyr::select(V1:V4)%>%
  dplyr::rename(Residence=V1, `1+ Doses of SP/Fansidar`=V2, `2+ Doses of SP/Fansidar`=V3, `3+ Doses of SP/Fansidar`=V4)%>%
  pivot_longer(cols = c(`1+ Doses of SP/Fansidar`:`3+ Doses of SP/Fansidar`), names_to = "Category", values_to = "Proportion")

readr::write_csv(IPTp_res, "table20_IPTp_usage_by_residence.csv")

IPTp_endem <- tbls[[72]]%>%
  slice(10:14)%>%
  dplyr::select(V1:V4)%>%
  dplyr::rename(`Endemicity zone`=V1, `1+ Doses of SP/Fansidar`=V2, `2+ Doses of SP/Fansidar`=V3, `3+ Doses of SP/Fansidar`=V4)%>%
  pivot_longer(cols = c(`1+ Doses of SP/Fansidar`:`3+ Doses of SP/Fansidar`), names_to = "Category", values_to = "Proportion")

readr::write_csv(IPTp_endem, "table20_IPTp_usage_by_endemicity_zone.csv")
```

### Table 20C: Use of intermittent preventive treatment (IPTp) by women during pregnancy by county	
```{r}
IPTp_county_implement <- tbls[[73]]%>%
  slice(5:18)%>%
  dplyr::select(V1:V4)%>%
  dplyr::rename(`County`=V1, `1+ Doses of SP/Fansidar`=V2, `2+ Doses of SP/Fansidar`=V3, `3+ Doses of SP/Fansidar`=V4)%>%
  pivot_longer(cols = c(`1+ Doses of SP/Fansidar`:`3+ Doses of SP/Fansidar`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Classification="IPTp implemented")
IPTp_county_not_implement <- tbls[[73]]%>%
  slice(21:53)%>%
  dplyr::select(V1:V4)%>%
  dplyr::rename(`County`=V1, `1+ Doses of SP/Fansidar`=V2, `2+ Doses of SP/Fansidar`=V3, `3+ Doses of SP/Fansidar`=V4)%>%
  pivot_longer(cols = c(`1+ Doses of SP/Fansidar`:`3+ Doses of SP/Fansidar`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Classification="IPTp not implemented")
IPTp_county <- rbind(IPTp_county_implement, IPTp_county_not_implement)%>%
  mutate(County=recode(County,"Tharaka-Nithi"="Tharaka Nithi", "Elgeyo/Marakwet"="Elgeyo Marakwet","Murang’a"="Muranga",
                       "Nairobi City"="Nairobi","Taita/Taveta"="Taita Taveta"))%>%
  mutate(Proportion=gsub("[()]", "", Proportion))
  

readr::write_csv(IPTp_county, "table20C_IPTp_usage_by_county.csv")
```

### Table 21: Children with fever and care seeking for, diagnosis of, and treatment of fever	
```{r}
fever_res <- tbls[[75]]%>%
  slice(6:7)%>%
  dplyr::select(V1,V2,V4,V5,V7)%>%
  dplyr::rename(Residence=V1, `Had a fever`=V2, `Treatment was sought`=V4, `Had blood taken for testing`=V5, `Received any ACT`=V7)%>%
  pivot_longer(cols = c(`Had a fever`:`Received any ACT`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Proportion=gsub("[()]", "", Proportion))%>%
  mutate(Proportion=ifelse(Proportion%in%"*",NA,Proportion))

readr::write_csv(fever_res, "table21_children_fever_by_residence.csv")

fever_endem <- tbls[[75]]%>%
  slice(10:14)%>%
  dplyr::select(V1,V2,V4,V5,V7)%>%
  dplyr::rename(`Endemicity zone`=V1, `Had a fever`=V2, `Treatment was sought`=V4, `Had blood taken for testing`=V5, `Received any ACT`=V7)%>%
  pivot_longer(cols = c(`Had a fever`:`Received any ACT`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Proportion=gsub("[()]", "", Proportion))%>%
  mutate(Proportion=ifelse(Proportion%in%"*",NA,Proportion))

readr::write_csv(fever_endem, "table21_children_fever_by_endemicity_zone.csv")

fever_wealth <- tbls[[75]]%>%
  slice(17:21)%>%
  dplyr::select(V1,V2,V4,V5,V7)%>%
  dplyr::rename(`Wealth quintile`=V1, `Had a fever`=V2, `Treatment was sought`=V4, `Had blood taken for testing`=V5, `Received any ACT`=V7)%>%
  pivot_longer(cols = c(`Had a fever`:`Received any ACT`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Proportion=gsub("[()]", "", Proportion))%>%
  mutate(Proportion=ifelse(Proportion%in%"*",NA,Proportion))

readr::write_csv(fever_wealth, "table21_children_fever_by_wealth_quintile.csv")
  
```

### Table 21C: Children with fever and care seeking for, diagnosis of, and treatment of fever by county

```{r}
fever_county <- tbls[[76]]%>%
  slice(5:51)%>%
  dplyr::select(V1,V2,V4,V5,V7)%>%
  dplyr::rename(`County`=V1, `Had a fever`=V2, `Treatment was sought`=V4, `Had blood taken for testing`=V5, `Received any ACT`=V7)%>%
  mutate(County=recode(County,"Tharaka-Nithi"="Tharaka Nithi", "Elgeyo/Marakwet"="Elgeyo Marakwet","Murang’a"="Muranga",
                       "Nairobi City"="Nairobi","Taita/Taveta"="Taita Taveta"))%>%
  pivot_longer(cols = c(`Had a fever`:`Received any ACT`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Proportion=gsub("[()]", "", Proportion))%>%
  mutate(Proportion=ifelse(Proportion%in%"*",NA,Proportion))

readr::write_csv(fever_county, "table21C_children_fever_by_county.csv")
```

### Table 22: Knowledge of, beliefs about, and diagnosis of tuberculosis	

```{r}
tb_age_women <- tbls[[77]]%>%
  slice(6:11)%>%
  dplyr::select(V1, V2, V4, V5)%>%
  dplyr::rename(Age=V1, `Have heard of TB`=V2, `Think everyone with TB has HIV`=V4, `Diagnosed in past 12 months`=V5)%>%
  pivot_longer(cols = c(`Have heard of TB`:`Diagnosed in past 12 months`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Participants="Women")
tb_age_men <- tbls[[77]]%>%
  slice(6:11)%>%
  dplyr::select(V1, V7, V9, V10)%>%
  dplyr::rename(Age=V1, `Have heard of TB`=V7, `Think everyone with TB has HIV`=V9, `Diagnosed in past 12 months`=V10)%>%
  pivot_longer(cols = c(`Have heard of TB`:`Diagnosed in past 12 months`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Participants="Men")
tb_age <- rbind(tb_age_women, tb_age_men)

readr::write_csv(tb_age, "table22_tb_by_age.csv")

tb_marital_women <- tbls[[77]]%>%
  slice(14:18)%>%
  dplyr::select(V1, V2, V4, V5)%>%
  dplyr::rename(`Marital status`=V1, `Have heard of TB`=V2, `Think everyone with TB has HIV`=V4, `Diagnosed in past 12 months`=V5)%>%
  pivot_longer(cols = c(`Have heard of TB`:`Diagnosed in past 12 months`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Participants="Women")
tb_marital_men <- tbls[[77]]%>%
  slice(14:18)%>%
  dplyr::select(V1, V7, V9, V10)%>%
  dplyr::rename(`Marital status`=V1, `Have heard of TB`=V7, `Think everyone with TB has HIV`=V9, `Diagnosed in past 12 months`=V10)%>%
  pivot_longer(cols = c(`Have heard of TB`:`Diagnosed in past 12 months`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Participants="Men")
tb_marital <- rbind(tb_marital_women, tb_marital_men)

readr::write_csv(tb_marital, "table22_tb_by_marital_status.csv")

tb_res_women <- tbls[[77]]%>%
  slice(21:22)%>%
  dplyr::select(V1, V2, V4, V5)%>%
  dplyr::rename(`Residence`=V1, `Have heard of TB`=V2, `Think everyone with TB has HIV`=V4, `Diagnosed in past 12 months`=V5)%>%
  pivot_longer(cols = c(`Have heard of TB`:`Diagnosed in past 12 months`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Participants="Women")
tb_res_men <- tbls[[77]]%>%
  slice(21:22)%>%
  dplyr::select(V1, V7, V9, V10)%>%
  dplyr::rename(`Residence`=V1, `Have heard of TB`=V7, `Think everyone with TB has HIV`=V9, `Diagnosed in past 12 months`=V10)%>%
  pivot_longer(cols = c(`Have heard of TB`:`Diagnosed in past 12 months`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Participants="Men")
tb_res <- rbind(tb_res_women, tb_res_men)

readr::write_csv(tb_res, "table22_tb_by_residence.csv")

tb_edu_women <- tbls[[77]]%>%
  slice(25:28)%>%
  dplyr::select(V1, V2, V4, V5)%>%
  dplyr::rename(`Education`=V1, `Have heard of TB`=V2, `Think everyone with TB has HIV`=V4, `Diagnosed in past 12 months`=V5)%>%
  pivot_longer(cols = c(`Have heard of TB`:`Diagnosed in past 12 months`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Participants="Women")
tb_edu_men <- tbls[[77]]%>%
  slice(25:28)%>%
  dplyr::select(V1, V7, V9, V10)%>%
  dplyr::rename(`Education`=V1, `Have heard of TB`=V7, `Think everyone with TB has HIV`=V9, `Diagnosed in past 12 months`=V10)%>%
  pivot_longer(cols = c(`Have heard of TB`:`Diagnosed in past 12 months`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Participants="Men")
tb_edu <- rbind(tb_edu_women, tb_edu_men)

readr::write_csv(tb_edu, "table22_tb_by_education.csv")
  
tb_wealth_women <- tbls[[77]]%>%
  slice(31:35)%>%
  dplyr::select(V1, V2, V4, V5)%>%
  dplyr::rename(`Wealth quintile`=V1, `Have heard of TB`=V2, `Think everyone with TB has HIV`=V4, `Diagnosed in past 12 months`=V5)%>%
  pivot_longer(cols = c(`Have heard of TB`:`Diagnosed in past 12 months`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Participants="Women")
tb_wealth_men <- tbls[[77]]%>%
  slice(31:35)%>%
  dplyr::select(V1, V7, V9, V10)%>%
  dplyr::rename(`Wealth quintile`=V1, `Have heard of TB`=V7, `Think everyone with TB has HIV`=V9, `Diagnosed in past 12 months`=V10)%>%
  pivot_longer(cols = c(`Have heard of TB`:`Diagnosed in past 12 months`), names_to = "Category", values_to = "Proportion")%>%
  mutate(Participants="Men")
tb_wealth <- rbind(tb_wealth_women, tb_wealth_men)

readr::write_csv(tb_wealth, "table22_tb_by_wealth.csv")
```

